\documentclass[10pt,a4paper]{article}

\usepackage[letterpaper,margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{fontawesome5}
\usepackage{hyperref}

\pagenumbering{gobble}

\usepackage{mathptmx}
\usepackage[T1]{fontenc}

\titleformat{\section}
{\bfseries\raggedright\large\MakeUppercase}
{}
{0em}
{}[\vspace{-3pt}\rule{\textwidth}{0.5pt}\vspace{2pt}]

\titlespacing{\section}{0pt}{12pt}{0pt}

\setlist[itemize]{
    leftmargin=1.1em,
    topsep=1pt,
    itemsep=0.5pt,
    parsep=0pt,
    label=\textbullet
}

\newcommand{\role}[2]{\textbf{#1} \hfill \textit{#2}}
\newcommand{\org}[2]{\textit{#1} \hfill #2}
\newcommand{\skillgroup}[2]{\textbf{#1:} #2}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black
}

\begin{document}

\begin{center}
    {\LARGE \textbf{Arjun M}} \\[3pt]
    {\small Electronics \& Communication Engineer} \\[2pt]
    {\small \faMapMarker* \hspace{0.3em} Thiruvananthapuram, Kerala \hspace{1.2em}
     \faPhone* \hspace{0.3em} +91 73564 64502 \hspace{1.2em}
     \faEnvelope \hspace{0.3em} \href{mailto:arjunmundakottu@gmail.com}{arjunmundakottu@gmail.com}} \\[2pt]
    {\small \faLinkedin \hspace{0.3em} \href{https://linkedin.com/in/arjunm11}{linkedin.com/in/arjunm11} \hspace{1.2em}
     \faGithub \hspace{0.3em} \href{https://github.com/vass112}{github.com/vass112}}
\end{center}

\vspace{2pt}

\section*{Professional Summary}

Electronics \& Communication Engineering graduate experienced in embedded systems, 5G infrastructure, wireless communications, drone development, and signal processing. Worked with live 5G NR equipment at IIST and Qualcomm-certified in 5G technologies. Co-founded a STEM education venture delivering 20+ technical workshops to 1000+ students. Expert in AI-augmented development, leveraging AI agents (opencode, Antigravity) to extract maximum output with minimal resources across firmware, software, and system design.

\section*{Experience}

\role{Co-Founder}{2024 -- Present} \\
\org{Nuke Labs}{}
\begin{itemize}
    \item Co-founded a technology and STEM education venture focused on drones, embedded systems, and hands-on engineering programs.
    \item Led 20+ technical workshops and training sessions on UAV systems, embedded systems, and programming for 1000+ students.
    \item Developed curriculum, managed project execution, partnerships, and technical mentorship activities.
\end{itemize}

\role{Project Intern -- 5G Testbed Lab}{Dec 2025} \\
\org{Indian Institute of Space Science and Technology (IIST)}{}
\begin{itemize}
    \item Worked with live 5G NR infrastructure including gNB, AMF, SMF, UPF, and MEC; deployed sensor nodes over a private 5G network and evaluated OTA performance.
    \item Studied antenna deployment, wireless link behaviour, signal integrity, and EMI; developed real-time monitoring pipelines using MEC infrastructure.
\end{itemize}

\role{Team Lead -- Global Evaluation Qualifier}{2024} \\
\org{NASA Space Apps Challenge}{}
\begin{itemize}
    \item Built a Python-based DSP pipeline for seismic signal extraction, filtering, and event classification; led the team to the Global Evaluation Round from 57,000+ participants.
\end{itemize}

\role{Chairperson, Student Branch Chapter}{2025 -- 2026} \\
\org{IEEE Signal Processing Society, Sree Buddha College of Engineering}{}
\begin{itemize}
    \item Organized embedded systems sessions, technical seminars, and project competitions.
\end{itemize}

\section*{Capstone Projects}

\role{Radar-Based Human Detection Rover}{2025 -- 2026}
\begin{itemize}
    \item Designed a search-and-rescue rover integrating an FMCW radar module with CFAR detection and Doppler processing for human presence detection through debris and low-visibility conditions.
    \item Developed an STM32-based embedded control system with real-time motor control, ultrasonic obstacle avoidance, and multi-threaded task scheduling.
\end{itemize}

\role{ESP32 Flight Controller}{2026}
\begin{itemize}
    \item Built a custom flight controller around the ESP32 with MPU6050 IMU, complementary-filter sensor fusion, and cascaded PID attitude stabilization.
    \item Implemented PWM ESC control for four brushless motors with failsafe logic for signal loss and low-battery conditions.
\end{itemize}

\role{DIY Radio Transmitter (ESP-NOW)}{2026}
\begin{itemize}
    \item Designed a custom RC transmitter using ESP32 with dual-joystick input, OLED telemetry, and a 3D-printed enclosure.
    \item Achieved sub-10ms control loop latency using ESP-NOW protocol with custom packet structure, CRC checking, and channel hopping.
\end{itemize}

\role{SCARA Pen Plotter}{2026}
\begin{itemize}
    \item Built a SCARA robot arm pen plotter with GRBL firmware, Flask web server, and browser-based G-code upload interface. \href{https://github.com/vass112/scara-pen-plotter}{GitHub}
\end{itemize}

\role{Radar Live UI}{2026}
\begin{itemize}
    \item Real-time radar visualization interface for RD03D sensor using Python/tkinter with SSE-based live updates and CSV data logging. \href{https://github.com/vass112/radar-live-ui}{GitHub}
\end{itemize}

\role{LD2450 TinyML -- Radar Motion Classifier}{2026}
\begin{itemize}
    \item Edge ML pipeline for LD2450 radar sensor: data capture, Keras model training, ESP32 deployment, and ESP-NOW telemetry dashboard. \href{https://github.com/vass112/ld2450-tinyml}{GitHub}
\end{itemize}

\role{Planetary Seismic Detection Pipeline}{2024}
\begin{itemize}
    \item Developed a Python DSP pipeline using STA/LTA triggering, bandpass filtering, and spectrogram analysis for seismic event detection and classification. \href{https://github.com/vass112/seismic-detection-ml}{GitHub}
\end{itemize}

\section*{Education}

\role{B.Tech Electronics \& Communication Engineering}{2022 -- 2026} \\
\org{Sree Buddha College of Engineering, Kerala}{CGPA: 7.85/10}
\begin{itemize}
    \item Coursework: Digital Signal Processing, Wireless Communication, Antenna Theory, Embedded Systems, Radar Signal Processing
\end{itemize}

\role{ISC (Physics, Chemistry, Mathematics)}{2022} \\
\org{St. Joseph's Convent English Medium School}{76.5\%}

\section*{Technical Skills}

\skillgroup{Wireless}{5G NR (gNB, AMF, SMF, UPF, MEC), Antenna Fundamentals, MIMO, Beamforming, OTA Testing, LoRa Mesh, SX1278, ESP-NOW} \\

\skillgroup{Programming}{Python, C, C++, Embedded C, MATLAB, AI-Assisted Development (opencode, Antigravity -- expert)} \\

\skillgroup{Embedded \& Signal Processing}{ESP32, STM32, Arduino, UART, SPI, I2C, PWM, ESC, IMU, GRBL / G-Code, ESP-NOW, PID Control, Flight Control, ESPHome, KiCad PCB Design; FFT, CFAR, Doppler Processing, Digital Filtering, Sensor Fusion; TinyML, TensorFlow / Keras} \\

\skillgroup{Tools \& Platforms}{Linux, KiCad, LTspice, Oscilloscope, Spectrum Analyzer, Git, VS Code, Jupyter, Flask, tkinter, Web UI, SSE, LaTeX} \\

\skillgroup{Networking}{Core Network Architecture, TCP/IP, MQTT, Network Slicing, Edge Computing / MEC} \\

\skillgroup{Development Methodology}{AI Agent-Enabled Development (software \& firmware), GitHub / Git Flow, Issue-Based Task Management, Validation-Driven Closed-Loop Development}

\section*{Certifications}

\role{Qualcomm Introductory 5G Certification}{Aug 2025}

\section*{Leadership \& Achievements}

\begin{itemize}
    \item Chairperson, IEEE SPS Student Branch Chapter (2025--2026); led workshops and events for 1000+ students
    \item NASA Space Apps Challenge 2024 Global Evaluation Qualifier
\end{itemize}

\vspace{6pt}
\begin{center}
\small English (Professional) \quad $|$ \quad Malayalam (Native) \quad $|$ \quad Hindi (Conversational)
\end{center}

\end{document}
